%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}
% \usepackage{ebgaramond}
% \usepackage{cochineal}
\usepackage{kpfonts}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}
\usepackage{fontawesome}
\usepackage{academicons}
\usepackage[dvipsnames]{xcolor}
%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
\usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\setlength{\footskip}{6pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-2pt}\scshape\raggedright\fontsize{16}{18}\selectfont
}{}{0em}{}[\color{black}\titlerule \vspace{-2pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeSubheadingTwo}[2]{
  \vspace{-2pt}\item
    \begin{tabular*}{1\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{[#2]} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{#2} \\
      \small#3 & \small #4 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumePubHeading}[2]{
  \vspace{1pt}\item
      \textbf{[#1]} #2  \\
    \vspace{1pt}
}

\newcommand{\resumePreprintHeading}[1]{
  \vspace{-2pt}\item
       #1  \\
    \vspace{-7pt}
}

\newcommand{\resumeSubheadingSix}[6]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \small#3 & \small #4 \\
      \small#5 & \small #6 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubheadingEight}[8]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \small#3 & \small #4 \\
      \small#5 & \small #6 \\
      \small#7 & \small #8 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-3pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------

\begin{center}
    \textbf{\Huge \scshape Yuxuan Yin} \\ \vspace{1pt}
    %\small 123-456-7890 $|$
    \href{mailto:y\_yin@ucsb.edu}{\faEnvelope\ y\_yin@ucsb.edu} $|$
    \href{https://linkedin.com/in/yuxuan-yin-793777237/}{\faLinkedinSquare\ LinkedIn} $|$
    % \href{https://zheng95z.github.io/}{\underline{zheng95z.github.io}} $|$
    \href{https://scholar.google.com/citations?hl=en&authuser=1&user=g6SyvToAAAAJ}{\faGoogle\ Google Scholar} $|$
    \href{callto:+18056371800}{\faMobile\ (+1) 805-637-1800} % $|$
    % {\faMapMarker\ Goleta, CA, 93117}
\end{center}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
   \resumeSubheading
      {University of California, Santa Barbara, USA}{Sep. 2021 -- \quad\quad\quad\quad\ \ }
      {Doctor of Philosophy in Electrical and Computer Engineering}{Advisor: Prof. Peng Li \href{https://scholar.google.com/citations?user=QYQUS7gAAAAJ\&hl=en\&authuser=2}{[\faGoogle]}}
    \vspace{4pt}\resumeSubheading
      {Tsinghua University, Beijing, China}{Aug. 2016 -- Jun. 2020}
      {Bachelor of Engineering in Electronic Engineering \& Bachelor of Science in Mathematics}{}
  \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------
\section{Internship Experience}
  \resumeSubHeadingListStart
  \resumeSubheading
        {Software Engineering Intern, Google, Sunnyvale, California}{Jun. 2025 -- Sep. 2025}
      {Research Topic: Large language models for cloud jobs' resource and runtime prediction}{Mentor: Shengke Zhou \href{https://www.linkedin.com/in/shengke-zhou/}{[\faLinkedinSquare]}}
  \resumeSubheading
        {AI Research Intern, NXP Automotive Processing, Austin, Texas}{Jun. 2024 -- Sep. 2024}
      {Research Topic: Conformal prediction for time series forecasting of PCB board aging}{Mentor: Chen He \href{https://www.linkedin.com/in/chen-he-119a5b3/}{[\faLinkedinSquare]}}
    \resumeSubheading
      {AI Research Intern, NXP Automotive Processing, Austin, Texas}{Jun. 2023 -- Sep. 2023}
      {Research Topic: Reliable interval prediction for chip performance}{Mentor: Chen He \href{https://www.linkedin.com/in/chen-he-119a5b3/}{[\faLinkedinSquare]}}


  \resumeSubHeadingListEnd


\section{Summary}
\begin{itemize}[leftmargin=0.14in]
    \setlength\itemsep{-0.5em}
    \item Ph.D. researcher in ML and agentic AI with hands-on experience building and evaluating LLM systems for real-world tasks, including long-context modeling, RAG-style reasoning, post-training (LoRA/finetuning).
    \item Strong foundation in reliable machine learning and decision-making under uncertainty, with published work in semi-supervised learning, Bayesian optimization, and conformal prediction at venues such as ICML, AAAI, DAC, and ICCAD.
\end{itemize}


%-----------PROJECTS-----------
\section{Selected Projects}

\subsection*{I. Agentic AI}
  \resumeSubHeadingListStart
    \resumeSubheadingTwo
      {1. LLMs for Cloud Jobs' Resource and Runtime Prediction}{Under Review}
      \resumeItemListStart
        \resumeItem{Built a LoRA-based supervised fine-tuning pipeline for predicting cloud-job resource and runtime requirements from job metadata, and improved numeric reliability with scientific-notation formatting and constrained decoding.}
      \resumeItemListEnd
    \resumeSubheadingTwo
      {2. Rotary Structural Embedding for Long-Context Understanding}{Ongoing}
      \resumeItemListStart
        \resumeItem{Designed a training-free extension to RoPE that learns per-chunk rotary angle adjustments from inter-chunk correlations, improving long-context reasoning quality on RAG and multi-turn dialogue settings.}
      \resumeItemListEnd
    \resumeSubheadingTwo
      {3. Analog Design Bayesian Optimization with In-Context Learning of Large Language Models}{ICCAD' 24}
      \resumeItemListStart
        \resumeItem{Developed a self-evolving LLM+BO agentic framework for analog circuit parameter optimization, combining LLM prior knowledge and in-context adaptation with the sample efficiency and rigor of Bayesian optimization.}
      \resumeItemListEnd
    \resumeSubheadingTwo
      {4. Graph-based Uncertainty Quantification of LLMs}{Under Review}
      \resumeItemListStart
        \resumeItem{Proposed a graph-based alignment method for uncertainty estimation in long-form LLM outputs by representing generations as fact graphs and quantifying semantic and structural disagreement.}
      \resumeItemListEnd
    % TSBO
    \resumeSubheadingTwo
      {5. High-Dimensional Bayesian Optimization with SSL and Unlabeled Sampling}{ICML' 24}
      \resumeItemListStart
        \resumeItem{Developed TSBO, a semi-supervised Bayesian optimization framework for data-efficient sequential design that selects high-value unlabeled samples and generates calibrated pseudo-labels via teacher-student feedback, achieving SOTA with up to 364.2x fewer labeled samples.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

% \subsection*{II. Semi-Supervised Learning (SSL)}
%   \resumeSubHeadingListStart
%     % TaMatch
%     \resumeSubheadingTwo
%       {1. Mitigation of Confirmation Bias in SSL: A Debiased Training Perspective}{Under Review}
%       \resumeItemListStart
%         \resumeItem{Addressed confirmation bias amplification in pseudo-label-based SSL algorithms by proposing a dynamic reweighting strategy based on learning status. This method balances the learning pace between easy and difficult classes, achieving the highest average accuracy across various challenging balanced and long-tail SSL datasets.}
%       \resumeItemListEnd
%   \resumeSubHeadingListEnd

\subsection*{II. Uncertainty Quantification}
  \resumeSubHeadingListStart
    \resumeSubheadingTwo
      {1. Graph-based Uncertainty Quantification of LLMs}{Under Review}
      \resumeItemListStart
        \resumeItem{Introduced a graph-based alignment framework for quantifying uncertainty in long-form LLM generations by modeling atomic facts and measuring semantic and structural inconsistencies.}
      \resumeItemListEnd
    \resumeSubheadingTwo
      {2. Data-Efficient Interval Prediction for Chip Performance Under Distribution Shifts}{DAC' 24}
      \resumeItemListStart
        \resumeItem{Proposed Calibrated Weighted CQR (CWCQR), a distribution-free interval prediction method with coverage guarantees under shift; on a 16nm automotive chip task, reduced interval length by 60\% at 90\% target coverage versus sigma-based baselines.}
      \resumeItemListEnd
    \resumeSubheadingTwo
      {3. Reliable Interval Prediction of Chip Performance via Conformalized Quantile Regression}{DATE' 24}
      \resumeItemListStart
        \resumeItem{Applied Conformalized Quantile Regression with a CatBoost predictor and on-chip monitors for reliable interval estimation in semiconductor manufacturing, achieving SOTA accuracy and data efficiency on a 5nm chip task.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------Publications-----------
\section{Publications}
  \resumeSubHeadingListStart
  \resumePubHeading{ITC' 25}
      {\textbf{Yuxuan Yin}, Rebecca Chen, Boxun Xu, Chen He, Peng Li. Transfer Learning for Minimum Operating Voltage Prediction in Advanced Technology Nodes: Leveraging Legacy Data and Silicon Odometer Sensing\ \href{https://arxiv.org/abs/2509.00035}{\textcolor{RawSienna}{[paper]}}}
  \resumePubHeading{VTS' 25}
      {\textbf{Yuxuan Yin}, Rebecca Chen, Chen He, Peng Li. Reliable Board-Level Degradation Prediction with Monotonic Segmented Regression under Noisy Measurement\ \href{https://ieeexplore.ieee.org/abstract/document/11022944}{\textcolor{RawSienna}{[paper]}}}
  \resumePubHeading{VTS' 25}
      {\textbf{Yuxuan Yin}, Rebecca Chen, Chen He, Peng Li. Data-Efficient Prediction of Minimum Operating Voltage via Inter- and Intra-Wafer Variation Alignment\ \href{https://arxiv.org/abs/2408.06254}{\textcolor{RawSienna}{[paper]}}}
  \resumePubHeading{ISCA' 25}
      {Boxun Xu, \textbf{Yuxuan Yin}, Vikram Iyer, Peng Li. Bishop: Sparsified Bundling Spiking Transformers on Heterogeneous Cores with Error-Constrained Pruning\ \href{https://dl.acm.org/doi/full/10.1145/3695053.3731063}{\textcolor{RawSienna}{[paper]}}}
  \resumePubHeading{ICCAD' 24}
      {\textbf{Yuxuan Yin}*, Yu Wang*, Boxun Xu, Peng Li. ADO-LLM: Analog Design  Bayesian Optimization with In-Context Learning of Large Language Models \ \href{https://dl.acm.org/doi/abs/10.1145/3676536.3676816}{\textcolor{RawSienna}{[paper]}}}
  \resumePubHeading{ICML' 24}
      {\textbf{Yuxuan Yin}, Yu Wang, Peng Li. High-dimensional Bayesian Optimization via Semi-supervised Learning with Optimized Unlabeled Data Sampling (\textbf{Spotlight})\ \href{https://proceedings.mlr.press/v235/yin24d.html}{\textcolor{RawSienna}{[paper]}}}
  \resumePubHeading{DAC' 24}
      {\textbf{Yuxuan Yin}, Rebecca Chen, Chen He, Peng Li. Data-Efficient Conformalized Interval Prediction of Minimum Operating Voltage Capturing Process Variations\ \href{https://dl.acm.org/doi/abs/10.1145/3649329.3657338}{\textcolor{RawSienna}{[paper]}}}
  \resumePubHeading{DATE' 24}
      {\textbf{Yuxuan Yin}, Xiaoxiao Wang, Rebecca Chen, Chen He, Peng Li. Reliable Interval Prediction of Minimum Operating Voltage Based on On-chip Monitors via  Conformalized Quantile Regression\ \href{https://ieeexplore.ieee.org/abstract/document/10546601}{\textcolor{RawSienna}{[paper]}}}
  \resumePubHeading{AAAI' 24}
      {Yu Wang, \textbf{Yuxuan Yin}, Karthik Suryanarayana, Jan Drgona, Malachi Schram, Mahantesh Halappanavar, Frank Liu, Peng Li. Semi-Supervised Learning of Dynamical Systems with Neural Ordinary Differential Equations: A Teacher-Student Model Approach\ \href{https://ojs.aaai.org/index.php/AAAI/article/view/29498}{\textcolor{RawSienna}{[paper]}}}
  \resumePubHeading{ITC' 23}
      {\textbf{Yuxuan Yin}, Rebecca Chen, Chen He, Peng Li. Domain-Specific Machine Learning based Minimum Operating Voltage Prediction using On-Chip Monitor Data\ \href{https://ieeexplore.ieee.org/abstract/document/10351099}{\textcolor{RawSienna}{[paper]}}}
  \resumePubHeading{IMWUT' 21}
      {Habiba Farrukh, Tinghan Yang, Hanwen Xu, \textbf{Yuxuan Yin}, He Wang, Z Berkay Celik. S3: Side-Channel Attack on Stylus Pencil through Sensors\ \href{https://dl.acm.org/doi/abs/10.1145/3448085}{\textcolor{RawSienna}{[paper]}}}

  \resumeSubHeadingListEnd


\section{Preprints}
  \resumeSubHeadingListStart
  \resumePubHeading{Arxiv}
  {\textbf{Yuxuan Yin}, Shengke Zhou, Yunjie Zhang, Ajay Mohindra, Boxun Xu, Peng Li. Large Language Models for EDA Cloud Job Resource and Lifetime Prediction\ \href{https://arxiv.org/abs/2512.19701}{\textcolor{RawSienna}{[paper]}}}
  \resumePubHeading{Arxiv}
      {\textbf{Yuxuan Yin*}, Yu Wang*, Peng Li. Towards the Mitigation of Confirmation Bias in Semi-supervised Learning: a Debiased Training Perspective\ \href{https://arxiv.org/abs/2412.05540}{\textcolor{RawSienna}{[paper]}}}

  % \resumePubHeading{Arxiv}
  %     {Boxun Xu, Hejia Geng, \textbf{Yuxuan Yin}, Peng Li. DISTA: Denoising Spiking Transformer with Intrinsic Plasticity and Spatiotemporal Attention}

  \resumeSubHeadingListEnd


%
%
%-----------PROGRAMMING SKILLS-----------
% \section{Technical Skills}
%  \begin{itemize}[leftmargin=0.15in, label={}]
%     \small{\item{
%      \textbf{Programming Languages}{: C/C++, Python} \\
%      \textbf{Softwares/Platforms/Libraries}{: Unity, Unreal Engine 4, PBRT, Mitsuba, OptiX, CUDA, PyTorch, TensorFlow} \\
%      \textbf{Research Tools}{: LaTex, Adobe Products (Photoshop, Illustrator, Premiere, etc.), Blender} \\
%     }}
%  \end{itemize}

%-------------------------------------------
\end{document}
